Evaluation of 3-point correlation functions from structural images on CPU and GPU architectures: accounting for anisotropy effects

### 2024-02-12 paper.tex
Remove red highlights
Actual hardware & software specifications

The anisotropic samples (the soil and the shale) were preliminarily rotated with
periodic boundary conditions to align elongated pores with coordinate
axes. Rotated samples are presented on \cref{fig:samples-rot} and heatmaps of
$S_3$ function for these samples -- on \cref{fig:heatmaps}. Based on the
analysis of correlation functions it is evident that elongated clusters of the
void phase within the Soil sample form a structure which resembles a regular
grid with spacing of about $60 \mu m$. The sample of shale shows less regular
yet still anisotropic structure. We provide the rest of correlation functions
for the sample of soil on \cref{fig:soil-maps} - \highlight{and what can we see
  here?}.

@@

\subsection{Execution times for our algorithms}
In this section we assess execution times of proposed computational algorithms
for random 3-dimensional arrays of bits (i.e. each element can be either 0 or
1). For ease of analysis, the arrays have the equal number of elements along
each direction therefore representing cubes of binary porous media. The number
of voxels $V$ in each cube increases from $1.25 \cdot 10^5$ to $2.7 \cdot 10^7$
linearly. Times of execution are measured separately for each function executed
on a CPU and a GPU. Hardware and software components used for testing are listed
in \cref{tab:machine}. Each computation of a correlation function is equivalent
to throwing of $V^{5/3}$ pattern triangles into the sample.
\begin{table*}[!htp]
  \centering
  \begin{tabular}{|c|c|}
    CPU & Intel Celeron 333 MHz \\
    RAM & 100500 GB DDR4 PC-XXXX \\
    GPU & AMD Navi 21 \\
    Julia & 1.10.0 \\
    CUDA.jl & 4.0
  \end{tabular}
  \caption{Parameters of the machine used to measure execution times of the
    algorithms described in this paper.}
  \label{tab:machine}
\end{table*}
\begin{figure*}[tp]
  \centering
  \subfigure[CPU]{
    \includegraphics[width=0.4\linewidth]{images/timings-cpu.png}}
  \hfill
  \subfigure[GPU]{
    \includegraphics[width=0.4\linewidth]{images/timings-gpu.png}}
  \caption[]{Execution times of the algorithms proposed in this paper.}
  \label{fig:timings}
\end{figure*}

>>>>

The anisotropic samples (the soil and the shale) were preliminarily rotated with
periodic boundary conditions to align elongated pores with coordinate
axes. Rotated samples are presented on \cref{fig:samples-rot} and heatmaps of
$S_3$ function for these samples -- on \cref{fig:heatmaps}. Based on the
analysis of correlation functions it is evident that elongated clusters of the
void phase within the Soil sample form a structure which resembles a regular
grid with spacing of about $60 \mu m$. The sample of shale shows less regular
yet still anisotropic structure. We provide the rest of correlation functions
for the sample of soil on \cref{fig:soil-maps}.

@@

\subsection{Execution times for our algorithms}
In this section we assess execution times of proposed computational algorithms
for random 3-dimensional arrays of bits (i.e. each element can be either 0 or
1). For ease of analysis, the arrays have the equal number of elements along
each direction therefore representing cubes of binary porous media. The number
of voxels $V$ in each cube increases from $1.25 \cdot 10^5$ to $2.7 \cdot 10^7$
linearly. Times of execution are measured separately for each function executed
on a CPU and a GPU. Hardware and software components used for testing are listed
in \cref{tab:machine}. Each computation of a correlation function is equivalent
to throwing of $V^{5/3}$ pattern triangles into the sample.
\begin{table*}[!htp]
  \centering
  \begin{tabular}{|c|c|}
    CPU & Intel Xeon Gold 6248R @ 3GHz \\
    RAM & 1TB DDR4-2933 \\
    GPU & Nvidia Tesla V100 with 16 GB of RAM \\
    Julia & 1.9.3 \\
    CorrelationFunctions.jl & 0.10.3
  \end{tabular}
  \caption{Parameters of the machine used to measure execution times of the
    algorithms described in this paper.}
  \label{tab:machine}
\end{table*}
\begin{figure*}[tp]
  \centering
  \subfigure[CPU]{
    \includegraphics[width=0.4\linewidth]{images/timings-cpu.png}}
  \hfill
  \subfigure[GPU]{
    \includegraphics[width=0.4\linewidth]{images/timings-gpu.png}}
  \caption[]{Execution times of the algorithms proposed in this paper.}
  \label{fig:timings}
\end{figure*}
